---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)

```

```{css}

```

## Colours, Options and Respective Prices across Auckland Coffee Menus

With this report I will be looking at how does the colour of coffee menus vary across cafes in different areas in Auckland. Then I will be looking at if some areas are more likely to offer certain coffees than others, then I will be looking at the different mean prices for certain coffee types across Auckland.

```{r}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/1bRHSrO-g7kUvGF8ckZmYA0AAGdB6AaMuRhqnV_oFZo0/edit?usp=sharingv") %>%
  rename(cafe_name = 2,
         address = 3,
         area = 4,
         background = 5,
         text = 6,
         latte = 7,
         cappucino = 8,
         flatwhite = 9,
         mocha = 10,
         espresso = 11,
         longblack = 12,
         shortblack = 13,
         americano = 14,
         affogato = 15,
         macchiato = 16,
         icedlatte = 17,
         icedamericano = 18,
         icedmocha = 19,
         irishcoffee = 20,
         latte_pos = 21,
         latte_m = 22,
         latte_l = 23,
         latte_s = 24,
         cappucino_pos = 25,
         cappucino_m = 26,
         cappucino_l = 27,
         cappucino_s = 28,
         flatwhite_pos = 29,
         flatwhite_m = 30,
         flatwhite_l = 31,
         flatwhite_s = 32,
         mocha_pos = 33,
         mocha_m = 34,
         mocha_l = 35,
         mocha_s = 36,
         espresso_pos = 37,
         espresso_m = 38,
         espresso_l = 39,
         espresso_s = 40,
         longblack_pos = 41,
         longblack_m = 42,
         longblack_l = 43,
         longblack_s = 44,
         shortblack_pos = 45,
         shortblack_m = 46,
         shortblack_l = 47,
         shortblack_s = 48,
         americano_pos = 49,
         americano_m = 50,
         americano_l = 51,
         americano_s = 52,
         affogato_pos = 53,
         affogato_m = 54,
         affogato_l = 55,
         affogato_s = 56,
         macchiato_pos = 57,
         macchiato_m = 58,
         macchiato_l = 59,
         macchiato_s = 60,
         icedlatte_pos = 61,
         icedlatte_m = 62,
         icedlatte_l = 63,
         icedlatte_s = 64,
         icedamericano_pos = 65,
         icedamericano_m = 66,
         icedamericano_l = 67,
         icedamericano_s = 68,
         icedmocha_pos = 69,
         icedmocha_m = 70,
         icedmocha_l = 71,
         icedmocha_s = 72,
         irishcoffee_pos = 73,
         irishcoffee_m = 74,
         irishcoffee_l =75,
         irishcoffee_s = 76)



logged_data %>%
  ggplot() +
  geom_bar(aes(y = area, fill = background)) +
  labs(title = "Menu Colours Across Auckland",
       subtitle = "Are some menu colours more prominent in some areas than rather others?",
       caption = "Source: Me",
       x = "# of Menus Recorded",
       y = "Areas")


```
```{r}
logged_data %>%
  ggplot() +
  geom_bar(aes(y = area, fill = macchiato)) +
  labs(title = "Macchiatos in Auckland",
       subtitle = "Are some areas of Auckland more likely to offer a Macchiato than others?",
       caption = "Source: Me",
       x = "# of Menus Recorded",
       y = "Areas")
```

```{r}
paste0("The lowest mean medium price for a coffee, is a short black, with a mean price of $", mean(logged_data$shortblack_m, na.rm = TRUE) %>% round(2), " and the highest mean medium price for a coffee is an iced mocha, with a mean price of $", mean(logged_data$icedmocha_m, na.rm = TRUE) %>% round(2))

paste0("The cheapest short black you can find is only $", min(logged_data$shortblack_m, na.rm = TRUE)," while the most expensive iced mocha you can get is $", max(logged_data$icedmocha_m, na.rm = TRUE))

paste0("On average you will find that the short black is the ", mean(logged_data$shortblack_pos, na.rm = TRUE) %>% round(), "th coffee offered on a menu, while the iced mocha is on average the ", mean(logged_data$icedmocha_m, na.rm = TRUE) %>% round(), "th coffee offered.")
```
